Progress Report on the ``Adult Database'' analysis

### 2009-11-11 report/paper.tex
More dataset information.
Dataset URL.

@@

>>>>

The data set is divided in two groups: the train set with 32561 records and the test set with 16281 entries.

@@

There are 3620 records with missing values. The attributes that contain missing values are: \textbf{Workclass}, \textbf{Occupation} and \textbf{Native-country}.

This data set is available in the following URL: \url{ftp://ftp.ics.uci.edu/pub/machine-learning-databases/adult}.
